### 2021-01-22 proposals/TESS_GI_cycle04/tessgi_gully_cycle4.tex
Making headway on the TESS proposal for spot contrast

\usepackage{caption}
\usepackage{subcaption}
\usepackage{cancel}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Some Useful Abbreviations %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tess}{{\it TESS}}
\newcommand{\jwst}{{\it JWST}}
\newcommand{\kepler}{{\it Kepler}}
\newcommand{\ktwo}{{K2}}
\newcommand{\hst}{{\it HST}}
\newcommand{\msun}{$M_{\odot}$}
\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\re}{$R_{\oplus}$}
\newcommand{\me}{$M_{\oplus}$}
\newcommand{\rj}{$R_{\textrm{\scriptsize Jup}}$}
\newcommand{\mj}{$M_{\textrm{\scriptsize Jup}}$}
\newcommand{\ms}{m~s$^{-1}$}

@@

\section{Introduction}

@@

\section{Analysis Plan}

@@

Starspots emit light, which is often parameterized as \emph{spot contrast}, $c$, where 0 means the spots are non-emitting, and $c=1$ means the spot matches the specific intensity of the ambient photosphere.  Spot contrast is wavelength dependent ($c_\lambda$) and can be thought of as possessing a characteristic spot temperature, $T_{spot}<T_{phot}$ that parameterizes the wavelength dependence of the contrasts.  The analysis technique proposed here leverages the different wavelength dependence of the \kepler\ and \tess\ system throughputs to directly measure the ratio of the spot contrasts in their respective bandpasses.  The spot contrast ratio---evaluated at these two pairs of bandpasses---provides a unique solution\footnote{Operationally, integrating the specific intensity $I_\lambda(T_{spot})$ over the system throughputs produces the expected contrast ratios.  For now we assume $I_\lambda(T_{spot})$ can be approximated as a cooler stellar photosphere, such as the \texttt{PHOENIX} model grid \cite{2013A&A...553A...6H}, an inexact but adequate assumption for the large bandpasses.} to $T_{spot}(\mathrm{SpT},\;P_{\mathrm{rot}})$.  \newline \newline
\textbf{Spot-induced modulation amplitudes depend on contrast.}

@@

@@

\begin{figure}[hbt!]
\includegraphics[width=0.95\textwidth]{figures/multi_panel.pdf}
\caption{\texttt{A)} Schematic of a planet ($R_p = 0.1 R_\star$) transiting a star with unocculted starspots as the star moves from left to right.  \texttt{B)} The resulting transit depth shows a systematic bias and a wavelength dependence due to starspots. \texttt{C)} Illustration of TLSE, \texttt{D)} Prediction for \tess\ amplitudes (colorful contours) relative to the \kepler\ sample (gray shaded background contours and black points) for $4000 < T_{phot} (K) < 4500$ \cite{2014ApJS..211...24M}.}
\label{fig:predictAmps}
\end{figure}

@@

\section{Technical Feasibility}

>>>>

\usepackage[svgnames]{xcolor}
\definecolor{darkgrey}{RGB}{83, 92, 104}

\usepackage[font={color=ocre,bf}]{caption}
\usepackage{subcaption}
\usepackage{cancel}
\usepackage{wrapfig}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Some Useful Abbreviations %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tess}{{\it TESS}}
\newcommand{\jwst}{{\it JWST}}
\newcommand{\kepler}{{\it Kepler}}
\newcommand{\ktwo}{{\it K2}}
\newcommand{\hst}{{\it HST}}
\newcommand{\msun}{$M_{\odot}$}
\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\re}{$R_{\oplus}$}
\newcommand{\me}{$M_{\oplus}$}
\newcommand{\rj}{$R_{\textrm{\scriptsize Jup}}$}
\newcommand{\mj}{$M_{\textrm{\scriptsize Jup}}$}
\newcommand{\ms}{m~s$^{-1}$}

@@

@@

\section{Analysis Plan: Compare \tess\ and \ktwo\ amplitudes}

@@

Starspots emit light, which is often parameterized as \emph{spot contrast}, $c$, where $0$ means the spots are completely black compared to the bright photosphere, and $c=0.3$ means the spot has 30\% the flux per-unit-surface-area of the pristine photosphere.  Hypothetically, a contrast of unity would mean the starspot blends into ambient photosphere, its border vanishing entirely.  Spot contrast is wavelength dependent ($c_\lambda$). It has a spectrum of its own, starting close to zero in the blue/visible, and approaching perhaps 40\% in the near-IR; the exact prescription remains an active research area \cite{2005LRSP....2....8B}.  Zeeman splitting and other magnetic phenomena are secondary to the mere fact that starspots appear as cooler-than-average regions on the stellar surface.

Starspot flux can be parameterized by labeling the emission components with a characteristic temperatures $T_\text{spot}<T_\text{phot}$.  The spot and ambient photosphere spectra depend only on those temperatures: $S(T_\text{spot})$ and $S(T_\text{phot})$.  The wavelength-dependent spot contrast is then simply the ratio of the spot spectrum to the ambient photosphere spectrum:  $c_\lambda = \frac{S(T_\text{spot})}{ S(T_\text{phot})}$.

Figure \ref{fig:filtercurve} shows an illustration of wavelength dependent spot contrast for a hypothetical M0V star with $T_\text{phot}=3800\;$K, and with $T_\text{spot}=3300\;$K.  We employ \texttt{PHOENIX} synthetic spectral models \cite{2013A&A...553A...6H}, accessed at these temperatures.  The contrast ascends from near 0.01 at $\lambda=500\;$nm, to 0.15 at 1 $\mu$m.  By 2.3 $\mu$m, the contrast has peaked at 0.3.  The overlapping \kepler\ and \tess\ system throughputs overplotted on Figure \ref{fig:filtercurve} indicate that---on average---the starspot contrast is a lower number for \kepler\ than for \tess.  Starspots look blacker in \kepler\ and \ktwo\ than they do in TESS.  The understanding of wavelength dependent starspot contrast is not novel--- it has driven the design of precision radial velocity (PRV) spectrographs to the near-IR, where the deleterious effect of starspots on RV jitter is lessened.  \textbf{The key innovation of this proposal stems from the vast number of sources with existing \ktwo\ data that \tess\ will observe in Cycle 4.  This proposal aims to quantify precisely the starspot contrast differences between the \tess\ and \kepler\ wavelength bands.}  We re-iterate that the extent to which nature produces starspot spectra resembling the prescription in Figure \ref{fig:filtercurve} remains an unknown, and is the main thrust of the proposed work effort.

System-throughput-weighted contrast spectra can be integrated over the illustrated filter curves to yield exact estimates for contrasts in these two bands.  For this M0V example, we obtain $c_{\ktwo}\sim0.02-0.3$ and $c_{\tess}\sim0.1$.  Starspots appear about three to five times darker in \kepler\ and \ktwo\ than they do in \tess\.  We define the ratio of starspot contrasts of \tess\ compared to \kepler\ as $\mathcal{R}\equiv \frac{c_{\tess}}{c_{\ktwo}}$.  This proposal will measure the ratio of starspot contrast in the \tess\ bandpass compared to the \ktwo\ bandpass for a vast number of stars observed by both missions.

illustrates the relative system throughputs of \tess\ and \kepler.

The analysis technique proposed here will systematically measure the ratio of starspot contrast between $\lambda = 550$ nm and $850$ nm by taking advantage of the different wavelength dependence of the \kepler\ and \tess\ system throughputs.

\captionsetup[figure]{font={color=darkgrey,md},textfont={small,singlespacing,md},labelfont={bf,normalsize,color=Black},labelformat={simple},labelsep=period,name={Figure}}

\begin{figure}[hbt!]
    \includegraphics[width=0.95\textwidth]{figures/contrast_spectrum.pdf}
    \caption{Illustration of starspot contrast as seen in \tess\ and \kepler. }
    \label{fig:filtercurve}
\end{figure}

The spot contrast ratio---evaluated at these two pairs of bandpasses---provides a unique solution Operationally, integrating the specific intensity $I_\lambda(T_{spot})$ over the system throughputs produces the expected contrast ratios.  For now we assume $I_\lambda(T_{spot})$ can be approximated as a cooler stellar photosphere, such as the \texttt{PHOENIX} model grid \cite{2013A&A...553A...6H}, an inexact but adequate assumption for the large bandpasses. to $T_{spot}(\mathrm{SpT},\;P_{\mathrm{rot}})$.  \newline \newline
\textbf{Spot-induced modulation amplitudes depend on contrast.}

@@

\begin{wrapfigure}[23]{r}[10pt]{2.6in}
    \vspace{0mm}
    \begin{center}
    \includegraphics[width=2.6in]{figures/fig1.pdf}
    \caption{Expected signal strength of starspot contrast for the same stars measured in \tess\ and \kepler. }
    \label{fig:expected}
    \vspace{0mm}
\end{center}
\end{wrapfigure}

@@

@@

\section{Technical Feasibility: Consistency is key}
